Proposed Solution

### 2017-01-25 CAV17/secs/trans.tex
trans

Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. For a $\ptype$ with $|\tau_i|$ 
we denote $c_i$, and $*$ is shorthand for all basic types. When there is no evidence for a type $\tau$ we call this empty type ({\scriptsize EMPTY}). Initially, before we count any type, all types are set to empty. 
In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.

@@

Taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}. The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$. By setting $M=3, N=1$, we resolve it to \texttt{bar}$::bool$.

>>>>

Fig.~\ref{fig:ptypes} provides a fragment of a calculus for type judgments for deriving Boolean equality rules with probabilistic types.
We use the notation, $\ptype \models p$, to denote a probabilistic type whose counts hold on the predicate $p$. 
For a probabilistic type, $\ptype$, we use the notation $|\tau_i|$ to select from $\ptype$, the $c_i$.
We use $*$ as a wildcard selector for all basic types in a $\ptype$.
When there is no evidence for a type $\tau$ we call this the empty type ({\scriptsize EMPTY}). 
Initially, all keywords are set to the empty set.
In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \ptype \in \tilde{\mathcal{T}}$ can be resolved to a basic type with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.

@@

Taking these type inference rules above, we can run an example inference on the sample training set in Figure~\ref{fig:tset}.
The result is the probabilistic type \texttt{bar}$:[bool=3,int=1]$.
If in this example, the user had set $M=3, N=1$, we resolve the probabilistic type of \texttt{bar} to \texttt{bar}$::bool$.

\ruzica{Mark, please argue better about this}
